Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-24 R0V0.tex
Changes on the introduction to focus more on the large-scale problem

\mypara Over the years, methods for the design of controllers for dynamical systems has developed different techniques, according to the vector field that describes the system structure. One of the main underlying concepts employed for the synthesis of feedback laws is Lyapunov's stability theory \cite{Bhatia1970,Rouche:1977}. In terms of computation, controller design problems are often translated in terms of optimization.

\mypara For linear systems, controller design methods include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}. The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}. In the case of nonlinear systems, design approaches include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}. These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}. In terms of numerical computation, often the techniques employed for feedback synthesis include sum-of-squares (SOS) optimization \cite{Parrilo2003}.

@@

\mypara The drawback of methods such as CCMs, $H_\infty$ optimization and LQR is that, when the system under consideration has many states (large scale), it does not scale well. This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions). In general, the case is worse, for nonlinear systems.

@@

\mypara For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions). The case can be even worse, when structural constraints are considered.

@@

\mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem. Although this is one of its main advantages over the search of control-Lyapunov functions, it does not scale well.

>>>>

\mypara Over the years, methods for the design of distributed controllers for large-scale systems have developed different techniques, according to the vector field that describes the system structure. For linear systems, controller design problems are often translated in terms of optimization.

\mypara Numerical methods to design linear controllers include $H_\infty$ optmization \cite{Doyleetal1992} and LQR \cite{Hespanha:2009}. The design problems are usually formulated in terms of linear matrix inequalities (LMIs) and semidefinite programming \cite{Boyd1994,DullerudPaganini2000}. In the case of nonlinear systems, design approaches are generally analytic and include high-gain  \cite{GrognardSepulchreBastin1999}, backstepping \cite{Krstic1995}, and forwarding \cite{MazencPraly96}. These methods depend on the structure of the vector field and may fail to be applied when appropriate conditions are not met \cite{SteinShiromoto2013a}.

@@

\mypara One of the drawbacks of numerical methods is that, when the system under consideration has a large number of states, it does not scale well. This is due to the fact that the stability verification of a linear system with $n$ states may require a function with $n^2$ terms (see \cite{Rantzer2015} for the case of linear systems and Lyapunov functions). In general, the case is worse, for nonlinear systems.

@@

\mypara For nonlinear systems, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions). The case can be even worse, when structural constraints are considered.

@@

\mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem. Although this is one of its main advantages over the search of control-Lyapunov functions, it cannot handle systems with a large number of systems, in general.
